---
title: "Week3"
author: "Lizzy Nickell"
date: "5/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(readr)        
library(dplyr)       
library(ggplot2)
library(tidyr)
library(sf)
library(terra)
```

```
Task 1
```{r}
caro60 <- read.csv("~/Dropbox/INN/ZHAW/PTED/Week 3/Week3/caro60.txt")
View(caro60)

caro <- caro60 %>%
  mutate(
    nMinus3 = sqrt((lag(E,3)-E)^2+(lag(N,3)-N)^2),    #-3 minutes
    nMinus2 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2),   # distance to pos -2 minutes
    nMinus1 = sqrt((lag(E,1)-E)^2+(lag(N,1)-N)^2),   # distance to pos -1 minute
    nPlus1  = sqrt((E-lead(E,1))^2+(N-lead(N,1))^2), # distance to pos +1 mintue
    nPlus2  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2),  # distance to pos +2 minutes
    nPlus3  = sqrt((E-lead(E,3))^2+(N-lead(N,3))^2)  # distance to pos +3 minutes
  )
  
```
Task 2
```{r}
#Add mean column
caro <- caro %>%
  rowwise() %>%
  mutate(
    stepMean = mean(c(nMinus3, nMinus2, nMinus1,nPlus1,nPlus2, nPlus3))
  ) %>%
  ungroup() 
  
summary(caro)
#Mean of stepMean is 6.9

caro <- caro %>% 
  ungroup() %>%
  mutate(static = stepMean < mean(stepMean, na.rm = TRUE))
```
Task 3
```{r}
caro%>%
  ggplot(aes(E, N, color = static))  +
  geom_path() +
  geom_point() +
  coord_fixed() +
  theme(legend.position = "right")
```
Task 4
```{r}
rle_id <- function(vec){
x <- rle(vec)$lengths 
as.factor(rep(seq_along(x), times=x)) 
}

caro <- caro %>% 
  mutate(segment_id = rle_id(static))

caro %>%
 ggplot(aes(E, N, color = segment_id))  +
   geom_path() +
   geom_point() +
   coord_fixed() +
   theme(legend.position = "right")  
   
caro %>%
  group_by(segment_id) %>% 
  filter(n() == 5)
  
  
caro %>%
 ggplot(aes(E, N, color = segment_id))  +
   geom_path() +
   geom_point() +
   coord_fixed() +
   theme(legend.position = "right")    
```

Task 5
```{r}
pedestrian <- read_csv("pedestrian.txt")

pedestrian %>%
  ggplot(aes(x=E, y=N, color=as.factor(TrajID) )) + 
  geom_path()+
  geom_point() +  
  facet_wrap(~TrajID) +
  theme(legend.position="none")
  
#6 trajectories, different speeds, and some outliers.  
```

Task 6
```{r}
library(SimilarityMeasures)


```

